# Appendix {.supplementary}

## Appendix A. Data curation {#sec-app-a .unnumbered}

This appendix describes the data construction in detail.
@cameron2015 provide guidance on standard errors that we rely on
throughout. Summary statistics are reported in @apxatbl-summary and a
coverage map in @apxafig-coverage.

::: {#apxatbl-summary}

```{r}
demo |>
  select(Income = income, Age = age, Education = educ) |>
  summarise(across(everything(),
    list(Mean = mean, SD = sd, Min = min, Max = max,
         N = ~ sum(!is.na(.x))))) |>
  tidyr::pivot_longer(everything(),
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
  mutate(across(c(Mean, SD, Min, Max), \(x) round(x, 1))) |>
  kable(format = "latex", booktabs = TRUE, linesep = "",
        align = c("l", rep("r", 5))) |>
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 9)
```

Summary statistics for the analysis sample.

:::

::: {.tblnotes}
*Notes:* Author calculations from the simulated XYZ Household Survey
panel constructed in the `setup` chunk. Income is reported in 2020
USD. The analysis sample comprises
`r format(nrow(demo), big.mark = ",")` observations across
`r length(unique(demo$state))` states.
:::

A second appendix table reports balance across treatment status:

::: {#apxatbl-balance}

```{r}
demo |>
  group_by(treat) |>
  summarise(Income = mean(income), Age = mean(age),
            Education = mean(educ), N = n()) |>
  mutate(treat = if_else(treat == 1, "Treated", "Control")) |>
  rename(Group = treat) |>
  mutate(across(c(Income, Age, Education), \(x) round(x, 1))) |>
  kable(format = "latex", booktabs = TRUE, linesep = "",
        align = c("l", rep("r", 4))) |>
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 9)
```

Balance check across treatment and control groups.

:::

::: {.tblnotes}
*Notes:* Group means by treatment status, unweighted. Differences
across groups are small in magnitude but not jointly zero.
:::

The coverage of the survey across states is summarized in
@apxafig-coverage. We also display the joint distribution of age and
income as a two-panel figure (@apxafig-joint), where panel (a) shows
the age distribution and panel (b) shows the joint density.

::: {#apxafig-coverage}

```{r}
#| fig-width: 5
#| fig-height: 3
demo |>
  count(state) |>
  ggplot(aes(x = reorder(state, n), y = n)) +
  geom_col(fill = "#4a7ab3", width = 0.7) +
  geom_text(aes(label = n), hjust = -0.2, size = 2.5) +
  coord_flip(clip = "off") +
  labs(x = "State", y = "Sample observations") +
  expand_limits(y = max(table(demo$state)) * 1.1) +
  theme_minimal(base_size = 9)
```

Sample coverage by state.

:::

::: {#apxafig-joint}

```{r}
#| fig-width: 6
#| fig-height: 2.6
library(patchwork)
p_age <- ggplot(demo, aes(x = age)) +
  geom_histogram(bins = 25, fill = "#4a7ab3", color = "white") +
  labs(x = "Age (years)", y = "Count", subtitle = "(a) Age distribution") +
  theme_minimal(base_size = 8) +
  theme(plot.subtitle = element_text(face = "bold", size = 8))

p_hex <- ggplot(demo, aes(x = age, y = income)) +
  # geom_bin2d works with base ggplot2 (no extra `hexbin` package).
  geom_bin2d(bins = 18) +
  scale_fill_gradient(low = "#dfe9f3", high = "#1f4e7a") +
  labs(x = "Age (years)", y = "Income (USD)", fill = "Count",
       subtitle = "(b) Age-income joint density") +
  theme_minimal(base_size = 8) +
  theme(plot.subtitle = element_text(face = "bold", size = 8),
        legend.key.size = unit(0.3, "cm"))

p_age + p_hex
```

Joint distribution of age and income — (a) marginal age, (b) joint density with income.

:::

::: {.tblnotes}
*Notes:* Panel (a) shows the marginal age distribution; panel (b)
shows a hex-binned joint density of age and income. Both panels use
the full analysis sample.
:::

## Appendix B. Robustness {#sec-app-b .unnumbered}

This appendix collects robustness exercises. The headline robustness
table is @apxbtbl-robust; an alternative specification is reported in
@apxbtbl-altspec, the wide event-study table appears in
@apxbtbl-event, and a sensitivity plot is shown in
@apxbfig-sensitivity. As in @abadie2017 we cluster at the relevant
unit of treatment assignment.

::: {#apxbtbl-robust}

```{r}
modelsummary(
  list("Baseline" = baseline,
       "+ Controls" = controls,
       "+ State FE" = state_fe),
  coef_map = c("treat" = "Policy X", "age" = "Age", "educ" = "Education"),
  gof_omit = "AIC|BIC|Log|F|RMSE|R2 Adj.",
  fmt = 3, stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  output = "kableExtra"
) |>
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 9)
```

Robustness of the main estimate to alternative specifications.

:::

::: {.tblnotes}
*Notes:* Standard errors clustered at the state level in parentheses.
Controls include age and education. State FE denotes state-level
fixed effects (10 states). *** $p<0.01$, ** $p<0.05$, * $p<0.1$.
:::

::: {#apxbtbl-altspec}

```{r}
# Toy "IV" and "matching" — for demo purposes
iv_fit    <- lm(income ~ treat + age + educ, data = demo)  # placeholder
match_fit <- lm(income ~ treat + age + educ, data = demo |> slice_sample(n = 800))

modelsummary(
  list("IV" = iv_fit, "Matching" = match_fit),
  coef_map = c("treat" = "Policy X"),
  gof_omit = "AIC|BIC|Log|F|RMSE|R2 Adj.",
  fmt = 3, stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  output = "kableExtra"
) |>
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 9)
```

Alternative identification strategies.

:::

::: {.tblnotes}
*Notes:* IV refers to an instrumental-variables design (placeholder
specification); Matching restricts the sample to a propensity-score
matched subset. Both report the same outcome equation as the
baseline.
:::

A wide event-study table sits awkwardly in portrait orientation, so
we rotate it. @apxbtbl-event shows the dynamic coefficients
$\hat\theta_k$ for $k \in \{-3, ..., +3\}$ (with $k=-1$ omitted as
the reference period).

::: {.landscape}

::: {#apxbtbl-event}

```{r}
# Build a wide synthetic event-study table with state-by-period FE columns
event_tab <- tibble(
  k = c(-3, -2, -1, 0, 1, 2, 3),
  est_base = c(-0.012, 0.008, NA_real_, 0.118, 0.124, 0.131, 0.129),
  se_base  = c(0.041, 0.038, NA_real_, 0.040, 0.041, 0.043, 0.046),
  est_ctrl = c(-0.010, 0.005, NA_real_, 0.115, 0.121, 0.128, 0.126),
  se_ctrl  = c(0.039, 0.036, NA_real_, 0.038, 0.039, 0.041, 0.044),
  est_fe   = c(-0.008, 0.004, NA_real_, 0.113, 0.119, 0.126, 0.124),
  se_fe    = c(0.044, 0.041, NA_real_, 0.045, 0.046, 0.048, 0.050),
  est_w    = c(-0.014, 0.007, NA_real_, 0.116, 0.122, 0.130, 0.128),
  se_w     = c(0.040, 0.037, NA_real_, 0.039, 0.040, 0.042, 0.045),
  est_l    = c(-0.011, 0.009, NA_real_, 0.119, 0.125, 0.132, 0.130),
  se_l     = c(0.042, 0.039, NA_real_, 0.041, 0.042, 0.044, 0.047)
)

fmt_pair <- function(est, se) {
  ifelse(is.na(est), "(omitted)",
         sprintf("%.3f (%.3f)", est, se))
}

event_tab |>
  transmute(
    `Relative period ($k$)` = paste0("$k = ", k, "$"),
    Baseline             = fmt_pair(est_base, se_base),
    `+ Controls`         = fmt_pair(est_ctrl, se_ctrl),
    `+ State FE`         = fmt_pair(est_fe,   se_fe),
    `Weighted`           = fmt_pair(est_w,    se_w),
    `Log-income`         = fmt_pair(est_l,    se_l)
  ) |>
  kable(format = "latex", booktabs = TRUE, escape = FALSE, linesep = "",
        align = c("l", rep("c", 5))) |>
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 9) |>
  add_header_above(c(" " = 1, "Specification" = 5))
```

Event-study coefficients for relative periods $k \in \{-3, \ldots, +3\}$.

:::

::: {.tblnotes}
*Notes:* Each cell reports the estimated $\hat\theta_k$ from
@eq-baseline with standard errors in parentheses. $k=-1$ is omitted
as the reference period. Weighted uses sampling weights;
Log-income uses $\log(1+Y)$ as the dependent variable. Sample as in
@apxatbl-summary.
:::

:::

A coefficient plot of the dynamic estimates is shown in
@apxbfig-sensitivity.

::: {#apxbfig-sensitivity}

```{r}
#| fig-width: 5
#| fig-height: 3
event_tab |>
  filter(!is.na(est_base)) |>
  mutate(low = est_base - 1.96 * se_base,
         hi  = est_base + 1.96 * se_base) |>
  ggplot(aes(x = k, y = est_base)) +
  geom_hline(yintercept = 0, color = "grey60", linewidth = 0.3) +
  geom_vline(xintercept = -0.5, color = "grey60", linewidth = 0.3, linetype = 2) +
  geom_errorbar(aes(ymin = low, ymax = hi), width = 0.15, color = "#1f4e7a") +
  geom_point(size = 1.5, color = "#1f4e7a") +
  scale_x_continuous(breaks = -3:3) +
  labs(x = "Relative period (k)", y = expression(hat(theta)[k])) +
  theme_minimal(base_size = 9)
```

Event-study coefficients, baseline specification.

:::

::: {.tblnotes}
*Notes:* Markers report $\hat\theta_k$; whiskers denote 95 percent
confidence intervals constructed from state-clustered standard
errors. Dashed line marks the omitted reference period ($k=-1$).
:::

```{=latex}
\FloatBarrier
```

## Appendix References {.unnumbered}

::: {#refs-appendix}
:::
