```{r setup}
#| include: false
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.align = "center", fig.width = 5.5, fig.height = 3.5,
  dpi = 300, dev = "pdf"
)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)
library(modelsummary)
library(broom)

# Reproducible toy data used throughout the demo so figures/tables
# are computed (not placeholders).
set.seed(20260518)
n <- 1200
demo <- tibble(
  id      = seq_len(n),
  state   = sample(LETTERS[1:10], n, replace = TRUE),
  age     = round(rnorm(n, 38, 12)),
  educ    = pmax(0, round(rnorm(n, 12, 3))),
  treat   = rbinom(n, 1, 0.45),
  income0 = rnorm(n, 4250, 1100)
) |>
  mutate(income = income0 + 380 * treat - 10 * age + 95 * educ + rnorm(n, 0, 500))

baseline <- lm(income ~ treat, data = demo)
controls <- lm(income ~ treat + age + educ, data = demo)
state_fe <- lm(income ~ treat + age + educ + factor(state), data = demo)
```

# Introduction

This manuscript demonstrates a workflow that combines two Quarto
techniques. First, the `multibib` Lua filter splits the bibliography
into a main list and an appendix list, following @smith2020 and
@angrist2009. Second, Quarto 1.4+ custom cross-reference kinds let us
number appendix tables independently — see @apxatbl-summary in
Appendix A and @apxbtbl-robust in Appendix B for examples that are
cross-referenced from the main text.[^pkg-note]

[^pkg-note]: All tables and figures in this demo are computed from a
simulated dataset of `r format(n, big.mark = ",")` observations
generated in the `setup` chunk; the empirical numbers should be
read as illustrative.

A second paragraph illustrates that the document supports normal
paragraph breaks. The economics literature has documented effects of
policy X on outcome Y across a wide variety of settings, including
labor markets, education, and health. Our contribution is twofold.
First, we provide new evidence using a richer panel than has been
available previously. Second, we develop a tractable estimator that
nests the workhorse two-way fixed-effects design as a special case.

The remainder of the paper proceeds as follows. Section 2 describes
the data and estimation strategy. Section 3 presents the main
results. Section 4 discusses external validity and the role of
alternative mechanisms. Section 5 concludes. All proofs, data
construction details, and robustness exercises are collected in the
appendices.

# Methods

We rely on standard econometric tools [@wooldridge2010]. Let $Y_{it}$
denote the outcome of interest for unit $i$ in period $t$, and let
$D_{it} \in \{0, 1\}$ be a binary indicator for treatment exposure.
The baseline specification is

$$
Y_{it} = \alpha_i + \lambda_t + \beta \, D_{it} + X_{it}' \gamma + \varepsilon_{it},
$$ {#eq-baseline}

where $\alpha_i$ and $\lambda_t$ are unit and time fixed effects,
$X_{it}$ is a vector of time-varying controls, and $\varepsilon_{it}$
is an idiosyncratic error term.[^id-fn] Under the standard
parallel-trends assumption, the coefficient $\beta$ in @eq-baseline
identifies the average treatment effect on the treated.

[^id-fn]: We use $i$ for unit (typically individual or firm) and $t$
for period. The notation follows @angrist2009.

A more flexible variant that we report in robustness exercises
replaces the single treatment indicator with a fully interacted set
of relative-time dummies:

\begin{align}
Y_{it} = \alpha_i + \lambda_t + \sum_{k = -K, k \neq -1}^{K} \theta_k \, \mathbb{1}\!\{t - E_i = k\} + X_{it}' \gamma + \varepsilon_{it},
\end{align}

where $E_i$ is the treatment-adoption date for unit $i$ and $\theta_k$
traces the dynamic path of the treatment effect. Standard errors are
clustered at the unit level throughout, following the recommendations
of @cameron2015 and @abadie2017 — see Appendix B for further
discussion.

Three additional comments on the estimation strategy are worth
flagging. First, identification rests on the absence of
contemporaneous shocks that are differentially correlated with
treatment status across units. We probe this assumption in Appendix B
using a placebo exercise with lagged treatment dummies. Second, the
controls $X_{it}$ are restricted to variables that are arguably
predetermined relative to $D_{it}$; including endogenous controls
would re-introduce the very bias the fixed-effects design is meant to
purge. Third, the sample is constructed from administrative records
described in Appendix A; differences in coverage across regions are
small but non-trivial, and we accommodate them with sampling weights.

# Results

The main result is summarized in @tbl-main. Note the table is numbered
"Table 1" — the appendix tables use a separate counter and start at
A1 and B1.

```{r}
#| label: tbl-main
#| tbl-cap: "Main results — effect of policy X on income"
modelsummary(
  list("Baseline" = baseline, "+ Controls" = controls),
  coef_map = c("treat" = "Policy X", "age" = "Age", "educ" = "Education"),
  gof_omit = "AIC|BIC|Log|F|RMSE|R2 Adj.",
  fmt = 3, stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  output = "kableExtra"
) |>
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 9)
```

The headline point estimate of
$\hat{\beta} = `r round(coef(baseline)["treat"], 2)`$ corresponds to
roughly a `r format(round(coef(baseline)["treat"], 0), big.mark = ",")`
USD increase in annual income for treated observations, relative to
the untreated counterfactual. The estimate is precisely measured
(standard error of `r round(summary(baseline)$coefficients["treat","Std. Error"], 1)`)
and statistically distinguishable from zero at conventional levels.

Magnitudes are economically meaningful. To benchmark them, note that
a one-standard-deviation change in education in our sample is
associated with a
`r round(coef(controls)["educ"] * sd(demo$educ), 0)`-USD difference
in income; the implied treatment effect is therefore roughly
`r round(coef(baseline)["treat"] / (coef(controls)["educ"] * sd(demo$educ)), 1)`
times the size of this correlational benchmark. Whether this
magnitude is plausible depends on one's prior about how much scope
remains for policy to move outcomes in this setting — a question we
return to in the discussion.

@fig-treat-effect plots the distribution of income for treated and
untreated observations to give a visual sense of the gap.

```{r}
#| label: fig-treat-effect
#| fig-cap: "Income distribution by treatment status"
#| fig-width: 5
#| fig-height: 3
ggplot(demo, aes(x = income, fill = factor(treat))) +
  geom_density(alpha = 0.5, color = NA) +
  scale_fill_manual(
    name = NULL,
    values = c("0" = "#7a9cc6", "1" = "#c45a4a"),
    labels = c("0" = "Untreated", "1" = "Treated")
  ) +
  labs(x = "Annual income (USD)", y = "Density") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom")
```

# Discussion

The findings are consistent with prior work [@angrist2009;
@smith2020]. Three threats to the interpretation deserve attention.

First, the parallel-trends assumption underlying @eq-baseline is, in
principle, untestable; in practice, we follow common practice and
inspect pre-trend coefficients in an event-study specification (see
Appendix B). The estimated pre-trends are small and statistically
indistinguishable from zero, but they are noisy enough that the
exercise is reassuring rather than dispositive.

Second, treatment exposure is correlated with several unit-level
characteristics that may, in principle, generate effect
heterogeneity. We document this heterogeneity in Appendix B and show
that the headline estimate is robust to dropping the most exposed
sub-population.

Third, the outcome Y is measured with non-trivial error in part of
the sample. Following @abadie2017 we report cluster-robust standard
errors throughout; we have also experimented with bootstrap
inference and the conclusions are unchanged.[^boot]

[^boot]: Wild cluster bootstrap with 999 replications, following
@cameron2015. Results are available on request.

# Conclusion

We have shown a reproducible Quarto setup that supports separate
bibliographies and multiple, cross-referenceable appendices. The
empirical exercise — illustrative as it is here — would in a real
paper carry implications for both academic understanding of mechanism
$M$ and for the design of policy P. We leave both for future work.

```{=latex}
\FloatBarrier
```

# References {.unnumbered}

::: {#refs-main}
:::
